### 2021-07-11 doc/thesis/chapters/dsp.tex
emphasis

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Demodulation of Broadcast FM}
\label{sec:demodulation-of-broadcast-fm}
%TODO: once FM is converted to AM, traditional AM DSP techniques can be employed

This section describes the demodulation of the information content of an FM broadcast channel, as it is used in commercial FM radio broadcasting.
The assumption here is, that the actual FM demodulation, as described in chapter \ref{sec:algorithms-for-digital-fm-demodulation} is already done correctly.
A frequency spectrum of the multiplex signal of an FM channel is shown in Fig.\ref{fig:fm_channel_baseband_freqs}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Emphasis and De-Emphasis}

TODO

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Demodulation of Broadcast FM}
\label{sec:demodulation-of-broadcast-fm}

This section describes the demodulation of the information content of an FM broadcast channel, as it is used in commercial FM radio broadcasting.
The assumption here is, that the actual FM demodulation, as described in chapter \ref{sec:algorithms-for-digital-fm-demodulation} is already done correctly, including the de-emphasis of the signal.

So at this point the FM signal is converted to an AM signal.
Thus, traditional AM DSP techniques can be employed to decode the FM broadcast channel.

A frequency spectrum of the multiplex signal of an FM channel is shown in Fig.\ref{fig:fm_channel_baseband_freqs}.
